\emeszida

### 2024-03-29 sigbovik/paper.tex
-

\section{Implications and Future Work}
This completely rewrites the history of modern computing and artificial intelligence.
Beyond focusing on important figures like Ada Lovelace and Grace Hopper we should be looking at pioneers thousands of years earlier like Enheduana the world's first known author \cite{Helle2023} and now the world's first known programmer.

>>>>

\section{Implications and Future Work}
This completely rewrites the history of modern computing and artificial intelligence.
In addition to focusing on important figures like Ada Lovelace and Grace Hopper we should be looking at pioneers thousands of years earlier like Enheduana the world's first known author \cite{Helle2023} and now the world's first known programmer.
